Body Image and Trikafta

### 2024-06-21 Emily Muther/body_image_trikafta.qmd
body image trikafta gender table

```{r}
#| label: demographics
df %>%
  select(Age, Gender, Race, Ethnicity) %>%
  tbl_summary(
    by = Gender,
    statistic = list(
      all_continuous() ~ "{mean} ({sd})"
    ),
    missing_text = "(Missing)"
  )
```

@@

```{r}
tbl_stack(
  list(
    mod %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod5 %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod7 %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod9 %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod3 %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod11 %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod13 %>%
      tbl_regression(exponentiate = T,intercept = T),
    mod15 %>%
      tbl_regression(exponentiate = T,intercept = T)
  ),
  group_header = c(
    rep("Elevated PHQ9", times = 4),
    rep("Elevated GAD7", times = 4)
  )
)
```

@@

```{r}
# Plot models together
p <- ggcoef_compare(list(
  "PHQ9" = mod,
  "PHQ9" = mod5, "PHQ9" = mod7, "PHQ9" = mod9, "GAD7" = mod3,
  "GAD7" = mod11, "GAD7" = mod13, "GAD7" = mod15
), exponentiate = T, add_reference_rows = F) +
  theme(text = element_text(size = 18))
p
# Save
ggsave("./Emily Muther/General/BodyImage_Trikafta/Reports/forest_plot.png",
       plot = p,width = 9,height = 6,units = "in")
```

>>>>

```{r}
#| label: demographics
normal_dist <- c("FRS_IdealBody")
df %>%
  select(
    PHQ9_Total, PHQ9_category, GAD7_Total, GAD7_category, FRStotal,
    FRS_IdealBody, FRS_ThinkyouLook, FRS_Category, Age, Gender, Race,
    Ethnicity
  ) %>%
  tbl_summary(
    by = Gender,
    type = list(c("FRStotal", "FRS_IdealBody", "FRS_ThinkyouLook") ~
      "continuous"),
    statistic = list(all_of(normal_dist) ~ "{mean} [{sd}]"),
    missing_text = "(Missing)"
  ) %>%
  add_overall() %>%
  add_p(
    test = list(all_of(normal_dist) ~ "t.test"),
    test.args = all_tests("wilcox.test") ~ list(exact = F)
  ) %>%
  separate_p_footnotes()
```

@@

```{r}
tbl_stack(
  list(
    mod %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod5 %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod7 %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod9 %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod3 %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod11 %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod13 %>%
      tbl_regression(exponentiate = T, intercept = T),
    mod15 %>%
      tbl_regression(exponentiate = T, intercept = T)
  ),
  group_header = c(
    rep("Elevated PHQ9", times = 4),
    rep("Elevated GAD7", times = 4)
  )
)
```

@@

```{r}
# Plot models together
p <- ggcoef_compare(list(
  "PHQ9" = mod,
  "PHQ9" = mod5, "PHQ9" = mod7, "PHQ9" = mod9, "GAD7" = mod3,
  "GAD7" = mod11, "GAD7" = mod13, "GAD7" = mod15
), exponentiate = T, add_reference_rows = F) +
  theme(text = element_text(size = 18))
p
# Save
ggsave("./Emily Muther/General/BodyImage_Trikafta/Reports/forest_plot.png",
  plot = p, width = 9, height = 6, units = "in"
)
```
